### 2017-07-10 Bright_Stars/Submission/submission2.tex
latest edits

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As a proof of principle, we have conducted a case study of five anti-cancer therapeutics. We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

@@

Data mining of public data sources coupled with network analysis enables the quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.  The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}. Reconstructing such networks enables a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame}. Such studies also (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research. The understanding of a therapeutic network, when coupled with information from clinical use of a therapeutic, also enables a recursive learning of the pathogenesis of the disease it is being used to treat, as has been noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.

Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}). They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-relevant research over a period greater than 100 years. These authors also suggest that thoughtful metrics derived from this concept could inform decision making by funders.

Extending the methodology to study additional cures and significant research advances is a logical next step. Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it supports an understanding of collaboration across networks as well as common features of science networks. Lastly, even if ambitious, scaling from case studies to mapping the entire domain of drug development is likely to be beneficial in planning, resource allocation and optimization of drug development activities.

To address these questions, we have built upon prior art for single networks to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks. Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery~\cite{bibWilliams}. For evaluation, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer. We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.

@@

\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics. \added[id=gc,remark={response to request from editor}]{The medical review document was copied from the Review section under Approval Date(s) and History, Letters, Labels, Reviews and cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references. If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.

\textbf{Patents} For each therapeutic\deleted[id=gc,remark=revise for clarity]{a single patent was identified that best represented the most relevant invention to the therapeutic at hand}\added[id=gc,remark=revised]{, the original patent for the therapeutic in question was identified using a combination of web searches, Google Patents, and the scientific literature}.  
\deleted[id=gc,remark=restate]{Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent...} \added[id=gc,remark={use example}]{For example, US5521184, the original patent for imatinib was assigned to the Ciba-Geigy Corporation in 1996 listing Zimmermann as inventor. Such manual identification is greatly assisted by a knowledge of the drug development field}. The non-patent citation list for a patent was copied from Google Patents~\cite{bibGooglePatents} and manually processed by searching the PubMed GUI for appropriate pmids \added[id=gc,remark={response to request from editor}] {using text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name. Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose and were used to generate the data in this study.

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs. The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study. [which are]

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}. Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.  Network visualization was performed using Cytoscape~\cite{bibCytoscape}.

@@

\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.

@@

\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{Here, we started with the literature directly cited in the approval process for five therapeutics, which are subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews that in turn contribute to the relevant literature. However, the only requirement of the current method is a starting set of articles. Any question premised upon the citation record and defined by a nucleus of articles can be addressed with this approach. The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent (IPS) cells  or CRISPR-Cas9. Furthermore, the method is generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios. The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, translational impact, etc. No matter the application, the method is implicitly time-dependent, allowing one to make historical comparisons and to set future goals. Importantly, our improvements to the method as presented here allow for the analysis across sets of articles in addition to within, supporting higher level interrogations of the crosstalk and collaborations that connect groups.}

In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history. Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research. The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs such as the Clinical and Translational Science Award (CTSA) Program. While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can also be viewed as another tool for citizen science. Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be valuable.

@@

 \section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow for critical comments and advice on formalizing definitions. We thank Sandeep Somaiya from NETE and Holly J. Falk-Krzesinski from Elsevier for their support of this project.

@@

@@

@@

\end{thebibliography}
\end{document}

>>>>

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As proof of principle, we have conducted a case study of five anti-cancer therapeutics \added[id=gc,remark={expanded Abstract to state question of interest}]{to identify the collaborations that resulted in the successful development of these therapeutics as well as nodes of influence in these networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

@@

Data mining of public data sources coupled with network analysis enables the quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.  The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}. Reconstructing such networks enables a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame}. Such studies also (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications, and (iii) help communicate the societal value of research. The understanding of a therapeutic network, when coupled with information from clinical use of a therapeutic, also enables a recursive learning of the pathogenesis of the disease it is being used to treat, as has been noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.

Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}). Key assumptions in constructing these networks were that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery. They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-relevant research over a period greater than 100 years. These authors also suggest that thoughtful metrics derived from this concept could inform decision making by funders. .

 \added[id=gc,remark={clarification of question as per journal request}]{In this study, we document the collaboration networks underlying five FDA-approved therapeutics for cancer. Building upon prior art for single networks we (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extend single network analysis to map publications and authors across multiple networks. In addition, we identify collaboration across networks and describe the role of funding and peer review outlining a system of layered collaborative activity in scientific discover. By studying additional cures and research advances, we also proceed towards scaling from single case studies to mapping the entire domain of drug development with the expectation that such knowledge will be beneficial in planning, resource allocation and optimization of drug development research. We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.}

@@

\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics. \added[id=gc,remark={response to request from editor}]{Under Approval Date(s) and History, Letters, Labels, Reviews, the medical review document was copied. Cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references. If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.

\textbf{Patents} For each therapeutic\deleted[id=gc,remark=revise for clarity]{a single patent was identified that best represented the most relevant invention to the therapeutic at hand}\added[id=gc,remark=revised]{, the original patent for the therapeutic in question was identified using a combination of web searches, Google Patents, and the scientific literature}.  
\deleted[id=gc,remark=restate]{Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent...} \added[id=gc,remark={use example}]{For example, US5521184, the original patent for imatinib was assigned to the Ciba-Geigy Corporation in 1996 listing Zimmermann as inventor. Manual identification is assisted by a knowledge of the field}. The non-patent citation list for a patent was copied from Google Patents~\cite{bibGooglePatents} and manually processed by searching the PubMed GUI for appropriate pmids \added[id=gc,remark={response to request from editor}] {using text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name. Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for this purpose and were used to generate the data in this study.

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs, the manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study. \added[id=gc,remark={clarification on network calcuation}]{For the gRBR metric (below), we counted only article and article in press when computing total researcher productivity.}

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and gRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and gRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}. Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}. \added[id=gc,remark={details of new computing procedures}] {The publicly available codes of the Williams study~\cite{bibLotia} were used as the basis for designing the codes used in our study. The previous codes were designed to generate graph objects and make use of graph methods such as breadth-first search (BFS) and depth-first search (DFS for graph traversal. In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the data with grants and peer review data. In the Williams study, assembly and analysis of each network took roughly 17 hours per drug, 10 of which are manual processing steps. While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.

@@

\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We built upon the work of Williams~\cite{bibWilliams} in several ways. Author disambiguation in the their code was not addressed beyond clustering by last name and first names. Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data. We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data. Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our code scales to larger article numbers and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}

@@

\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{In this study, we begin with the literature directly cited in the approval process for five therapeutics. The approval process for therapeutics is subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews, each of which cite relevant literature. However, the only requirement of the current method is a starting set of articles. The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent stem (iPS) cells~\cite{bibIPS}  or CRISPR-Cas9~\cite{bibCRISPR}. Thus, any question premised upon accessible citation records and defined by a nucleus of articles can be addressed with our approach. Furthermore, the method is also generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios. The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, and translational impact. No matter the application, the method is implicitly time-dependent, allowing one to make historical comparisons and to set future goals. Importantly, our improvements to the method as presented here allow for the analysis across sets of articles in addition to within, supporting higher level interrogations of the crosstalk and collaborations that connect groups.}

In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history. Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research. The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs. \deleted[id=gc,remark={delete in view of previous paragraph}]{such as the Clinical and Translational Science Award (CTSA) Program.} While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science. Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.

@@

 \section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions. We also thank Sandeep Somaiya from NETE and Holly J. Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.

@@

\bibitem{bibLotia}
Lotia, S., and Pico, A.P. 
\newblock {{Gladstone Bibliometrics}
\newblock https://github.com/ gladstone-institutes/bibliometrics/tree/1.0.1.

@@

\bibitem{bibIPS}
Takahashi K, Yamanaka S.
\newblock {{I}nduction of pluripotent stem cells from mouse embryonic and adult fibroblast cultures by defined factors}
\newblock  Cell. 2006. 25;126(4):663-76.

\bibitem{bibCRISPR}
Charpentier E, Doudna JA.
\newblock {{B}iotechnology: Rewriting a genome}
\newblock  Nature. 2013 7;495(7439):50-1. doi: 10.1038/495050a.

\end{thebibliography}

@@

\end{document}
